---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# missing.values

<!-- badges: start -->
<!-- badges: end -->

The goal of missing.values is to count the number of missing values from each column of a dataset grouped by one column.

## Installation

You can install the development version of missing.values like so:
```r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/missing.values")

```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(missing.values)
#This example computes the number of missing values in the `airquality` dataset grouped by the `cyl` #column. 

count_all_missing_by_group(airquality, Month)
```

This example has the same output as the last example, but shows off an alternative way of invoking the `count_all_missing_by_group()`: piping the dataset into the function. 

```{r} 
airquality |> count_all_missing_by_group(Month) 
```

The optional `.groups` argument allows us to keep the output grouped by the grouping column. See example below; notice how the output is a grouped tibble, rather than the ungrouped tibble output of the earlier examples. 

```{r} 
count_all_missing_by_group(airquality, Month, .groups = "keep")
```
